\documentclass[12pt]{article}

\newcommand{\blind}{1}
\pdfminorversion=4
\newcommand{\georddtitle}{
    A Bayesian Nonparametric Approach to Geographic Regression Discontinuity Designs:
    Do School Districts Affect NYC House Prices?
}
\input{preamble.tex}
% disable hyperlinks between documents
\newcommand{\autorefexternal}[1]{\autoref*{#1}}

\begin{document}
\doublespacing

\externaldocument{"supplementary_materials"}

\if0\blind
{
\title{
    \Large
    \bf
    \georddtitle
}
\author{\georddauthor}
\maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf \georddtitle}
\end{center}
  \medskip
} \fi
% \if1\blind
% {
    % \author{\vspace{-3em}}
% } \fi
\begin{abstract}
    Most research on regression discontinuity designs (RDDs) has focused on univariate cases, where only those units with a ``forcing'' variable on one side of a threshold value receive a treatment.
    Geographical regression discontinuity designs (GeoRDDs) extend the RDD to multivariate settings with spatial forcing variables.
    We propose a framework for analysing GeoRDDs, which we implement using Gaussian process regression. 
    This yields a Bayesian posterior distribution of the treatment effect at every point along the border.
    We address nuances of having a functional estimand defined on a border with potentially intricate topology, particularly when defining and estimating causal estimands of the local average treatment effect (LATE).
    The Bayesian estimate of the LATE can also be used as a test statistic
    in a hypothesis test with good frequentist properties, 
    which we validate using simulations and placebo tests.
    We demonstrate our methodology with a dataset of property sales in New York City,
    to assess whether there is a discontinuity in housing prices at the border between two school district.
    We find a statistically significant difference in price across the border between the districts with \(p\)=0.002, and estimate a 20\%  higher price on average for a house on the more desirable side.
\end{abstract}

\noindent%
{\it Keywords}: \georddkeywords
\vfill
\newpage

\input{geordd_raw}


\end{document}
