\documentclass[aoas,preprint]{imsart}

\RequirePackage[OT1]{fontenc}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{xr-hyper} % cross-references (between documents)
\usepackage{xcolor} % Allow colors to be defined
\usepackage{geometry} % Used to adjust the document margins
\usepackage{amsmath} % Equations
\usepackage{amssymb} % Equations
% The hyperref package gives us a pdf with properly built
% internal navigation ('pdf bookmarks' for the table of contents,
% internal cross-reference links, web links for URLs, etc.)
\usepackage[hyphens]{url}
\usepackage[hypertexnames=false]{hyperref}
\usepackage[title,toc]{appendix}
\newcommand{\georddtitle}{
    A Bayesian Nonparametric Approach to Geographic Regression Discontinuity Designs:
    Do School Districts Affect NYC House Prices?
}
\hypersetup{
    colorlinks=true,
    pdfborder=0 0 1,
    pdftitle=\georddtitle{},
    allcolors=[rgb]{0.00,0.38,0.59},
    allbordercolors=[rgb]{0.60,0.76,0.86}
}
\usepackage{natbib}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{pdflscape}

\startlocaldefs
\input{preamble.tex}
\newcommand{\autorefexternal}[1]{\autoref{#1}}
\endlocaldefs
\arxiv{arXiv:1807.04516}

\begin{document}
    \begin{frontmatter}
        \title{
            \georddtitle
        }
        \runtitle{
            A Bayesian Nonparametric Approach to Geographic RDDs
        }
    \begin{aug}
        \author{\fnms{Maxime} \snm{Rischard}\thanksref{m1}\ead[label=e1]{mrischard@g.harvard.edu}},
        \author{\fnms{Zach} \snm{Branson}\thanksref{m1}\ead[label=e2]{zbranson@g.harvard.edu}}
        \author{\fnms{Luke} \snm{Miratrix}\thanksref{m1}\ead[label=e3]{lmiratrix@g.harvard.edu}}
        \and
        \author{\fnms{Luke} \snm{Bornn}\thanksref{m2}\ead[label=e4]{lbornn@sfu.ca}}

        % \thankstext{t1}{This research was supported by the National Science Foundation under Grant No. 1461435.}
        % \thankstext{t2}{First supporter of the project}
        % \thankstext{t3}{Second supporter of the project}
        \thankstext{t1}{
            This research was supported by the National Science Foundation Graduate Research Fellowship Program under Grant No. 1144152, by the National Science Foundation under Grant No. 1461435, by DARPA under Grant No. FA8750-14-2-0117, by ARO under Grant No. W911NF- 15-1-0172, and by NSERC. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the National Science Foundation, DARPA, ARO, or NSERC.
        }
        \runauthor{M. Rischard et al.}

        \affiliation{{Harvard University}\thanksmark{m1}
                     and {Simon Fraser University}\thanksmark{m2}}
        \address{M. Rischard and Z. Branson \\
                 Department of Statistics\\
                 Harvard University\\
                 Cambridge, MA\\
                 USA \\
                \printead{e1}\\
                \phantom{E-mail:\ }\printead*{e2}
        }
        \address{Luke Miratrix \\
                 Graduate School of Education\\
                 Harvard University\\
                 Cambridge, MA\\
                 USA \\
                \printead{e3}
        }
        \address{Luke Bornn \\
                 Department of Statistics and Actuarial Science\\
                 Simon Fraser University\\
                 Burnaby, B.C.\\
                 Canada \\
                \printead{e4}
        }
    \end{aug}

    \begin{abstract}
        \input{geordd_abstract.tex}
    \end{abstract}

    \begin{keyword}[class=MSC]
    \kwd[Primary ]{60K35}
    \kwd{60K35}
    \kwd[; secondary ]{60K35}
    \end{keyword}

    \begin{keyword}
    \kwd{sample}
    \kwd{\LaTeXe}
    \end{keyword}

\end{frontmatter}
\input{geordd_raw}

\begin{appendices}
    \input{geordd_appendices}
\end{appendices}

\bibliographystyle{chicago}
\bibliography{GeoRDD}

%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
% https://tex.stackexchange.com/questions/168169/options-for-supplementary-materials-in-preprint-version-revtex-arxiv#169606
\pagebreak
\begin{center}
\phantomsection
    \addcontentsline{toc}{section}{Supplementary Materials}
    \bf 
    \LARGE
    Supplementary Materials
    \\*
    \large
    \georddtitle
\end{center}
%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{section}{0}
\newcommand{\sprefix}{S-}
\renewcommand{\theequation}{\sprefix\arabic{equation}}
\renewcommand{\thesection}{\sprefix\arabic{section}}
\renewcommand{\thefigure}{\sprefix\arabic{figure}}
\renewcommand{\thetable}{\sprefix\arabic{table}}

\input{supplementary_raw.tex}

\end{document}
